### 2023-11-06 Scripts/Manuscript/manuscript.Rmd
added the source script
added the data cleaning functions

```{r setup, include = FALSE}
# loading R libraries
library("papaja")
library("worcs")

@@

# Code below loads the processed data. The raw data was prepared for analysis in 'prepare_data.R.
# load_data(worcs_directory = "../../Data/AnalysisData")

@@

@@

@@

@@

>>>>

```{r setup, include = FALSE}
# loading R libraries
library(papaja)
library(worcs)
library(psych)

@@

# Code below loads the processed data. The raw data was prepared for analysis in 'prepare_data.R.
load_data()

@@

```{r Cleaning Replication Datasets Data}
##### Data already available, code does not need to be run!
### ML 1
# 1.3
data_1.3_clean <- cbind(as.factor(data_ml1[[5]]), data_ml1[22:29])
colnames(data_1.3_clean)[1] <- "g"
# 1.10
data_1.10_clean <- cbind(as.factor(data_ml1[[5]]), data_ml1[108:115])
colnames(data_1.10_clean)[1] <- "g"
# 1.11
data_1.11_clean <- cbind(as.factor(data_ml1[[5]]), data_ml1[73:76])
colnames(data_1.11_clean)[1] <- "g"
# 1.12.1
# not found
# 1.12.3
data_1.12.3.1_clean <- cbind(as.factor(data_ml1[[5]]), data_ml1[54:59])
colnames(data_1.12.3.1_clean)[1] <- "g"
data_1.12.3.2_clean <- cbind(as.factor(data_ml1[[5]]), data_ml1[60:65])
colnames(data_1.12.3.2_clean)[1] <- "g"

### ML 2
# 2.2
data_2.2_clean <- cbind(as.factor(data_2.2[[5]]), data_2.2[6:11])
colnames(data_2.2_clean)[1] <- "g"
# 2.3
# data does not appear suitable
# 2.4.1
data_2.4.1_clean <- cbind(as.factor(data_2.4.1[[5]]), data_2.4.1[6:11])
colnames(data_2.4.1_clean)[1] <- "g"
# 2.4.2
data_2.4.2_clean <- cbind(as.factor(data_2.4.2[[5]]), data_2.4.2[6:14])
colnames(data_2.4.2_clean)[1] <- "g"
# 2.8.2
data_2.8.2_clean <- cbind(as.factor(data_2.8.2[[6]]), data_2.8.2[9:13])
colnames(data_2.8.2_clean)[1] <- "g"
# 2.10.1
data_2.10.1_clean <- cbind(as.factor(data_2.10.1[[5]]), data_2.10.1[6:11])
colnames(data_2.10.1_clean)[1] <- "g"
# 2.12.1
data_2.12.1_clean <- cbind(as.factor(data_2.12[[5]]), data_2.12[c(6,7,8,9,10,31,32,33,34,35)]) 
data_2.12.1_clean[3465:6905,2:6] <- data_2.12.1_clean[3465:6905,7:11]
data_2.12.1_clean <- data_2.12.1_clean[1:6]
colnames(data_2.12.1_clean)[1] <- "g"
# 2.12.2
data_2.12.2_clean <- cbind(as.factor(data_2.12[[5]]), data_2.12[c(11,14,15,18,19,22,24,27,28,29,36,39,40,43,44,47,49,52,53,54)]) 
data_2.12.2_clean[3465:6905,2:11] <- data_2.12.2_clean[3465:6905,12:21]
data_2.12.2_clean <- data_2.12.2_clean[1:11]
colnames(data_2.12.2_clean)[1] <- "g"
# 2.12.3
data_2.12.3_clean <- cbind(as.factor(data_2.12[[5]]), data_2.12[c(12,13,16,17,20,21,23,25,26,30,37,38,41,42,45,46,48,50,51,55)]) 
data_2.12.3_clean[3465:6905,2:11] <- data_2.12.3_clean[3465:6905,12:21]
data_2.12.3_clean <- data_2.12.3_clean[1:11]
colnames(data_2.12.3_clean)[1] <- "g"
# 2.15
data_2.15_clean <- cbind(as.factor(data_2.15[[5]]), data_2.15[8:12])
colnames(data_2.15_clean)[1] <- "g"
# 2.19.1
# difficult to extract
# 2.19.2
# difficult to extract
# 2.20
data_2.20_clean <- cbind(as.factor(data_2.20[[5]]), data_2.20[6:45] - 1) 
data_2.20_clean[3729:7396,2:21] <- data_2.20_clean[3729:7396,22:41]
data_2.20_clean <- data_2.20_clean[1:21] 
colnames(data_2.20_clean)[1] <- "g"
# 2.23
data_2.23_clean <- cbind(as.factor(data_2.23[[5]]), data_2.23[c(7,8,12,13,15)])
colnames(data_2.23_clean)[1] <- "g"

### ML 3
# 3.2.1
data_3.2.1 <- cbind(as.factor(data_ml3[[1]]), data_ml3[77:86] - 1)
data_3.2.1.1_clean <- na.omit(data_3.2.1[1:6])
colnames(data_3.2.1.1_clean)[1] <- "g"
data_3.2.1.2_clean <- na.omit(data_3.2.1[c(1, 7:11)])
colnames(data_3.2.1.2_clean)[1] <- "g"
# 3.5
# data appears unusable
# 3.7.1
data_3.7.1_clean <- na.omit(cbind(as.factor(data_ml3[[1]]), data_ml3[38:42]))
colnames(data_3.7.1_clean)[1] <- "g"
# 3.7.2
data_3.7.2_clean <- na.omit(cbind(as.factor(data_ml3[[1]]), data_ml3[89:94]))
colnames(data_3.7.2_clean)[1] <- "g"
# 3.8.1
# a single measure was reported
# 3.8.2
data_3.8.2_clean <- na.omit(cbind(as.factor(data_ml3[[1]]), data_ml3[29:30])) 
colnames(data_3.8.2_clean)[1] <- "g"

### ML 5
# 5.1.1
data_5.1.1_clean <- cbind(as.factor(data_5.1[[2]]), data_5.1[13:33])
colnames(data_5.1.1_clean)[1] <- "g"
# 5.1.2
# difficult to separate .1 from .2
# 5.4
data_5.4_clean <- cbind(as.factor(data_5.4[[1]]), data_5.4[18:41])
colnames(data_5.4_clean)[1] <- "g"
# 5.5.1 & 5.5.2
# from this dataset it appears that this data will be difficult to use.
# 5.5.2
# also difficult to use
# 5.7 
data_5.7_clean <- cbind(as.factor(data_5.7[[3]]), data_5.7[c(25, 34, 35, 36, 37, 38, 39, 40, 41, 42)])
colnames(data_5.7_clean)[1] <- "g"
# 5.9.1
data_5.9.1_clean <- na.omit(cbind(as.factor(data_5.9.1[[4]]), data_5.9.1[c(79, 83, 87, 91, 95, 98, 101)]))
colnames(data_5.9.1_clean)[1] <- "g"

### to summarize
# total number of likely usable: 15 (1.10, 1.11, 1.12.3.1, 1.12.3.2, 2.10.1, 
# 2.12.1, 2.12.2, 2.12.3, 2.15, 2.23, 3.7.1, 3.7.2, 3.8.2, 5.7, 5.9.1)
# total number of maybe usable: 6 (1.3, 2.20, 3.2.1.1, 3.2.1.2, 5.1.1, 5.4)
# total alpha coefficient comparison usable: 3 
#                                           1.11: 0.82
#                                           3.7.2: 0.67
#                                           5.9.1: 0.84

### Saving to Intermediate Data Folder
closed_data(data = data_1.3_clean, filename = "Data/IntermediateData/data_1.3_clean.csv",
            codebook = "Data/IntermediateData/codebook_data_1.3_clean.Rmd", 
            value_labels = "Data/IntermediateData/value_labels_data_1.3_clean.yml", 
            synthetic = FALSE)

closed_data(data = data_1.10_clean, filename = "Data/IntermediateData/data_1.10_clean.csv",
            codebook = "Data/IntermediateData/codebook_data_1.10_clean.Rmd", 
            value_labels = "Data/IntermediateData/value_labels_data_1.10_clean.yml", 
            synthetic = FALSE)

closed_data(data = data_1.11_clean, filename = "Data/IntermediateData/data_1.11_clean.csv",
            codebook = "Data/IntermediateData/codebook_data_1.11_clean.Rmd", 
            value_labels = "Data/IntermediateData/value_labels_data_1.11_clean.yml", 
            synthetic = FALSE)

closed_data(data = data_1.12.3.1_clean, filename = "Data/IntermediateData/data_1.12.3.1_clean.csv",
            codebook = "Data/IntermediateData/codebook_data_1.12.3.1_clean.Rmd", 
            value_labels = "Data/IntermediateData/value_labels_data_1.12.3.1_clean.yml", 
            synthetic = FALSE)

closed_data(data = data_1.12.3.2_clean, filename = "Data/IntermediateData/data_1.12.3.2_clean.csv",
            codebook = "Data/IntermediateData/codebook_data_1.12.3.2_clean.Rmd", 
            value_labels = "Data/IntermediateData/value_labels_data_1.12.3.2_clean.yml", 
            synthetic = FALSE)

closed_data(data = data_2.10.1_clean, filename = "Data/IntermediateData/data_2.10.1_clean.csv",
            codebook = "Data/IntermediateData/codebook_data_2.10.1_clean.Rmd", 
            value_labels = "Data/IntermediateData/value_labels_data_2.10.1_clean.yml", 
            synthetic = FALSE)

closed_data(data = data_2.12.1_clean, filename = "Data/IntermediateData/data_2.12.1_clean.csv",
            codebook = "Data/IntermediateData/codebook_data_2.12.1_clean.Rmd", 
            value_labels = "Data/IntermediateData/value_labels_data_2.12.1_clean.yml", 
            synthetic = FALSE)

closed_data(data = data_2.12.2_clean, filename = "Data/IntermediateData/data_2.12.2_clean.csv",
            codebook = "Data/IntermediateData/codebook_data_2.12.2_clean.Rmd", 
            value_labels = "Data/IntermediateData/value_labels_data_2.12.2_clean.yml", 
            synthetic = FALSE)

closed_data(data = data_2.12.3_clean, filename = "Data/IntermediateData/data_2.12.3_clean.csv",
            codebook = "Data/IntermediateData/codebook_data_2.12.3_clean.Rmd", 
            value_labels = "Data/IntermediateData/value_labels_data_2.12.3_clean.yml", 
            synthetic = FALSE)

closed_data(data = data_2.15_clean, filename = "Data/IntermediateData/data_2.15_clean.csv",
            codebook = "Data/IntermediateData/codebook_data_2.15_clean.Rmd", 
            value_labels = "Data/IntermediateData/value_labels_data_2.15_clean.yml", 
            synthetic = FALSE)

closed_data(data = data_2.20_clean, filename = "Data/IntermediateData/data_2.20_clean.csv",
            codebook = "Data/IntermediateData/codebook_data_2.20_clean.Rmd", 
            value_labels = "Data/IntermediateData/value_labels_data_2.20_clean.yml", 
            synthetic = FALSE)

closed_data(data = data_2.23_clean, filename = "Data/IntermediateData/data_2.23_clean.csv",
            codebook = "Data/IntermediateData/codebook_data_2.23_clean.Rmd", 
            value_labels = "Data/IntermediateData/value_labels_data_2.23_clean.yml", 
            synthetic = FALSE)

closed_data(data = data_3.2.1.1_clean, filename = "Data/IntermediateData/data_3.2.1.1_clean.csv",
            codebook = "Data/IntermediateData/codebook_data_3.2.1.1_clean.Rmd", 
            value_labels = "Data/IntermediateData/value_labels_data_3.2.1.1_clean.yml", 
            synthetic = FALSE)

closed_data(data = data_3.2.1.2_clean, filename = "Data/IntermediateData/data_3.2.1.2_clean.csv",
            codebook = "Data/IntermediateData/codebook_data_3.2.1.2_clean.Rmd", 
            value_labels = "Data/IntermediateData/value_labels_data_3.2.1.2_clean.yml", 
            synthetic = FALSE)

closed_data(data = data_3.7.1_clean, filename = "Data/IntermediateData/data_3.7.1_clean.csv",
            codebook = "Data/IntermediateData/codebook_data_3.7.1_clean.Rmd", 
            value_labels = "Data/IntermediateData/value_labels_data_3.7.1_clean.yml", 
            synthetic = FALSE)

closed_data(data = data_3.7.2_clean, filename = "Data/IntermediateData/data_3.7.2_clean.csv",
            codebook = "Data/IntermediateData/codebook_data_3.7.2_clean.Rmd", 
            value_labels = "Data/IntermediateData/value_labels_data_3.7.2_clean.yml", 
            synthetic = FALSE)

closed_data(data = data_3.8.2_clean, filename = "Data/IntermediateData/data_3.8.2_clean.csv",
            codebook = "Data/IntermediateData/codebook_data_3.8.2_clean.Rmd", 
            value_labels = "Data/IntermediateData/value_labels_data_3.8.2_clean.yml", 
            synthetic = FALSE)

closed_data(data = data_5.1.1_clean, filename = "Data/IntermediateData/data_5.1.1_clean.csv",
            codebook = "Data/IntermediateData/codebook_data_5.1.1_clean.Rmd", 
            value_labels = "Data/IntermediateData/value_labels_data_5.1.1_clean.yml", 
            synthetic = FALSE)

closed_data(data = data_5.4_clean, filename = "Data/IntermediateData/data_5.4_clean.csv",
            codebook = "Data/IntermediateData/codebook_data_5.4_clean.Rmd", 
            value_labels = "Data/IntermediateData/value_labels_data_5.4_clean.yml", 
            synthetic = FALSE)

closed_data(data = data_5.7_clean, filename = "Data/IntermediateData/data_5.7_clean.csv",
            codebook = "Data/IntermediateData/codebook_data_5.7_clean.Rmd", 
            value_labels = "Data/IntermediateData/value_labels_data_5.7_clean.yml", 
            synthetic = FALSE)

closed_data(data = data_5.9.1_clean, filename = "Data/IntermediateData/data_5.9.1_clean.csv",
            codebook = "Data/IntermediateData/codebook_data_5.9.1_clean.Rmd", 
            value_labels = "Data/IntermediateData/value_labels_data_5.9.1_clean.yml", 
            synthetic = FALSE)

```

@@

```{r Cleaning Coded Data}
##### Data already available, code does not need to be run!
# Selecting the relevant rows and columns for the data
coded_data_initial_sel <- coded_data_initial_raw[3:160, 18:57]
coded_data_revised_sel <- coded_data_revised_raw[3:160, 18:38]
coded_data_vignette_raw <- coded_data_vignette_raw[3:160, 2]

# Combining the datasets
coded_data_full <- cbind(coded_data_initial_sel, 
                         cbind(coded_data_revised_sel, coded_data_vignette_raw))

# filtering out unnecessary double columns
coded_data_full <- cbind(coded_data_full[, 1:40], coded_data_full[, 45:62])

### creating the cleaned dataset using the functions in the source code 
coded_data_clean <- calculating(recoding(restructuring(fixing(
  renaming(coded_data_full)))))

### Saving to Intermediate Data Folder
# Splitting data into replication and original
coded_data_replications <- coded_data_clean[1:77,]
coded_data_original <- coded_data_clean[78:157,]

# difference in dataset row number is due to the fact that the moral foundations
# questionnaire in original 2.4 is reported using all 5 of its factors, whereas
# in replication 2.4 only the two overarching groups of binding and 
# individualizing foundations are described.
# For that reason a shortened original dataset will be used for any direct
# comparisons between original and replication coding.
coded_data_original_shortened <- coded_data_original[c(1:17, 19, 22:80),] 
coded_data_original_shortened[c(18,19),5] <- 
  c("individualizing moral foundations", "binding moral foundations")
coded_data_original_shortened[18,13] <- NA
coded_data_original_shortened[19,13] <- NA

# exporting cleaned data
open_data(data = coded_data_replications, filename = paste0(paste0(
  "Data/IntermediateData/", deparse(substitute(coded_data_replications))), ".csv"),
  codebook = paste0(paste0(
    "Data/IntermediateData/codebook_", 
    deparse(substitute(coded_data_replications))), ".Rmd"),
  value_labels = paste0(paste0(
    "Data/IntermediateData/value_labels_", 
    deparse(substitute(coded_data_replications))), ".yml"))

open_data(data = coded_data_original, filename = paste0(paste0(
  "Data/IntermediateData/", deparse(substitute(coded_data_original))), ".csv"),
  codebook = paste0(paste0(
    "Data/IntermediateData/codebook_", 
    deparse(substitute(coded_data_original))), ".Rmd"),
  value_labels = paste0(paste0(
    "Data/IntermediateData/value_labels_", 
    deparse(substitute(coded_data_original))), ".yml"))

open_data(data = coded_data_original_shortened, filename = paste0(paste0(
  "Data/IntermediateData/", deparse(substitute(coded_data_original_shortened))), ".csv"),
  codebook = paste0(paste0(
    "Data/IntermediateData/codebook_", 
    deparse(substitute(coded_data_original_shortened))), ".Rmd"),
  value_labels = paste0(paste0(
    "Data/IntermediateData/value_labels_", 
    deparse(substitute(coded_data_original_shortened))), ".yml"))

```

@@

```{r}

```

@@

```{r Check for Reliability and Validity Testability}
## Checking the measures to recalculate the reliability and factor analysis for.
## The question: "Are they psychometrics scales or not?", is key here.
View(coded_data_replications)

# Likely reliability: 1.10, 1.11, 1.12.3, 2.4.1, 2.4.2, 2.8.2, 2.10.1, 2.12.1, 
# 2.12.2, 2.12.3, 2.15, 2.19.2, 2.23, 3.7.1, 3.7.2, 3.8.1, 3.8.2, 5.7, 5.9.1
# Likely factor: 1.10, 1.11, 1.12.3, 2.4.1, 2.4.2, 2.8.2, 2.10.1, 2.12.1, 2.12.2,
# 2,12,3, 2.15, 2.19.2, 2.23, 3.7.1, 3.7.2, 3.8.1, 3.8.2, 5.7, 5.9.1
# Maybe reliability: 1.3, 1.12.1, 2.2, 2.3, 2.19.1, 2.20, 3.2.1, 3.5, 5.1.1, 
# 5.1.2, 5.4, 5.5.1, 5.5.2
# Maybe factor: 1.3, 1.12.1, 2.3, 2.19.1, 2.20, 3.2.1, 3.5, 5.1.1, 5.1.2, 5.4,
# 5.5.1, 5.5.2

# 1.9 is difficult, might be a scale as dv rather than voting behaviour.
```
